---
title: "writing_functions"
author: "cathy"
date: "2024-10-24"
output: html_document
---

```{r}
library(tidyverse)
library(rvest)
```

## writing my first function!!

as an example, here's a z-score computation
```{r}
x_vec = rnorm(n = 25, mean =10, sd = 3.5)

(x_vec - mean(x_vec)) / sd(x_vec)
```

now, i'll write a funciton to do this 
```{r}
z_score = function(x){
  
  if(!is.numeric(x)){
    stop("x need to be numeric")
  }
  if(length(x) < 5){
    stop("you need at least 5 numbers to compute the z score")
  }
  z = (x - mean(x)) / sd(x)
  
  return(z)
  
}

z_score(x = x_vec) #put every x i find in the fucntion, to x_vec
```

does this always work?
```{r, error = TRUE}
z_score(x = 3) #cannot do with only 1 number

z_score(x = c("My", "Name", "is", "Cathy")) # cannot apply characteristic

z_score(x = x_vec)
```

## New fucntion!

```{r}
mean_and_sd = function(x){
  
   mean_x = mean(x)
   sd_x = sd(x)
   
   out_df = 
     tibble(
       mean =mean_x,
       sd = sd_x
     )
  
  return(out_df)
  
  
}

mean_and_sd(x_vec)
```


## Check stuff using a simulation

```{r}
sim_df = 
  tibble(
    x = rnorm(30, 10, 5)
  )

sim_df |> 
  summarize(
  mean = mean(x),
  sd = sd(x)
)
```


Simulation function rto check samole mean and sd.

```{r}
sim_mean_sd = function(samp_size=30, true_mean=16, true_sd=4){
  
  sim_df = 
  tibble(
    x = rnorm(samp_size, true_mean, true_sd)
  )

  out_df= 
   sim_df |> 
   summarize(
   mean = mean(x),
   sd = sd(x)
   )
  
  return(out_df)
}
sim_mean_sd(samp_size=30, true_mean=4, true_sd=12) #can be put in different order

sim_mean_sd(30,16,2) #can also run successfully

sim_mean_sd(300) #can default in the function part, and rewrite another number.
```


##Revisit LoTR words

```{r}
fellowship_df =
  readxl::read_excel("data/LotR_Words.xlsx",range = "B3:D6") |> 
  mutate(move = "fellowship") |> 
  janitor::clean_names()

two_towers__df =
  readxl::read_excel("data/LotR_Words.xlsx",range = "F3:H6") |> 
  mutate(move = "two_towers") |> 
  janitor::clean_names()

return_king_df =
  readxl::read_excel("data/LotR_Words.xlsx",range = "J3:L6") |> 
  mutate(move = "return_king") |> 
  janitor::clean_names()

```

using function to do the same thing.
focus on which part need to be change, put into function

```{r}
lotr_import = function(cell_range, movie_title){
  
  movie_df =
    readxl::read_excel("data/LotR_Words.xlsx",range = cell_range) |> 
    mutate(movie = movie_title) |> 
    janitor::clean_names() |> 
    pivot_longer(
      female:male,
      names_to = "sex",
      values_to = "words"
    ) |> 
    select(movie, everything())
  
  return(movie_df)
  
}

lotr_df = 
  bind_rows(
    lotr_import("B3:D6", "fellowship"),
    lotr_import("F3:H6", "two_towers"),
    lotr_import("J3:L6", "return_king")
)

```


##NSDUH

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)

marj_table= 
 nsduh_html |> 
  html_table() |> 
  nth(4) |> 
  slice(-1) |> 
  mutate(drug = "marj")
  
cocaine_table= 
 nsduh_html |> 
  html_table() |> 
  nth(4) |> 
  slice(-1) |> 
  mutate(drug = "cocaine")
  
heroin_table= 
 nsduh_html |> 
  html_table() |> 
  nth(4) |> 
  slice(-1) |> 
  mutate(drug = "heroin")


```


Write function to do this in a simpler way

```{r}
nsduh_table_format = function(html, table_num, table_name){
  
  out_table =
    nsduh_html|> #here, the html is outside the R, need to find in website, 
                 #so, it's better be specific in 'function'part
    html_table() |> 
    nth(table_num) |> 
    slice(-1) |> 
    mutate(drug = table_name) |> 
    select(-contains("P Value"))

  
  return(out_table)
  
}

  bind_rows(
    nsduh_table_format (nsduh_html, 1, "marj"),
    nsduh_table_format (nsduh_html, 4, "cocaine"),
    nsduh_table_format (nsduh_html, 5, "heroin")
  )

```

```{r}
source("source/nsduh_table_format.R")
  bind_rows(
    nsduh_table_format (nsduh_html, 1, "marj"),
    nsduh_table_format (nsduh_html, 4, "cocaine"),
    nsduh_table_format (nsduh_html, 5, "heroin")
  )


```















